On Secure Delegation of SampBQP with a Classical Client

### 2020-02-08 bqp.tex
Add notes from Skype discussion

@@

\begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$ language $L$}
	\label{proto:BQP}
	Input: $x\in\set{0,1}^n$.
	\begin{enumerate}
		\item $\cV_1$:
			On input $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_x$, where $m=\poly(n)$, $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.

			\Ethan{How does this $\cV_1$ thing work?}
		\item The verifier sends $x$ to the prover.
		\item $\cP_2$:
			On input $x$, the prover applies an algorithm to generate $\rho\in\cB^{\otimes m}$.
		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $w$.
		\item $\cV_3$:
			On input $w$, the verifier generates and outputs either accept or reject using a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}

@@

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $x\in\set{0,1}^n$.
	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
	\begin{enumerate}
		\item The verifier, on input $x$ generates $\Lambda$ using $\cV_1$ of \cref{proto:BQP}.
			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
			It computes $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
			Finally, it sends $y$ and $evk$ to the prover
		\item The prover homomorphically evaluates $\cP_2$ of \cref{proto:BQP} on input $y$, generating $\sigma=\mathsf{QHE.Eval}(\cP_2, y)$.
			The prover sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext $\sigma$ according to $\Lambda'$, getting $ct$
			It applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
			On input $w$, it applies $\cV_3$ of \cref{proto:BQP} and outputs its result.
	\end{enumerate}
\end{protocol}

@@

	\Ethan{TODO PROOFREAD ME}
	Suppose for the sake of contradiction that some prover $\bbP'$ breaks the soundness of \cref{proto:BlindBQP}.

	We construct $\tilde\bbP$ a prover against the soundness guarantees in \cref{proto:BQP} as $(\bbV, \tilde\bbP)$.

	$\tilde\bbP$ simulates \cref{proto:BlindBQP} as $(\bbV', \bbP')$.

	When $\bbP'$ sends $\sigma$, $\tilde\bbP$ computes and sends $\rho=\mathsf{QHE.Dec}_{sk}(\sigma)$ to $\bbV$.

	$\bbV'$ has a non-negligible chance to accept after receiving $\sigma$.
	When that happens, $\cV(w)=\cV(\Lambda(\rho))=Acc$, so $\bbV$ would also accept after receiving $\rho$.
\end{prf}

>>>>

\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf for conventions. Mal. parties have stars, protos use Pi. Stuff like $r[(P(w), V )(1n ,(M, x, t))$ }

\Ethan{More notation, fix interfaces}

\Ethan{Fix up to proto 3 and proofs}

@@

\begin{protocol}{1-message $\QPIP_1$ protocol $\Pi_{MF} = (P_{MF}, V_{MF})$ for $\BQP$ language $L$ \Ethan{TODO use macros}}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The verifier generates $\Lambda \leftarrow \cV_1(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
		\Ethan{change $\cV_1$ to $\cV_{MF, 1}$}
		\item The prover generates a certificate state $\rho\leftarrow\cP_2(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit. Let $w \in \set{0,1}^n$ denote the measurement outcome. It verifies the measurement outcome and produces a decision  $o\leftarrow\cV_3(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cV_3$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}

@@

\begin{protocol}{Blind Protocol $\Pi_{blind} = (P_{blind}, V_{blind}$) for $\BQP$ \Ethan{Define and use macros later}}
	\label{proto:BlindBQP}
	Let $x\in\set{0,1}^n$.
	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
	\begin{enumerate}
		\item The verifier, on input $x$ generates $\Lambda$ using $\cV_1$ of \cref{proto:BQP}.
			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
			It computes $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
			Finally, it sends $y$ and $evk$ to the prover
		\item The prover homomorphically evaluates $\cP_2$ of \cref{proto:BQP} on input $y$, generating $\sigma=\mathsf{QHE.Eval}(\cP_2, y)$.
			The prover sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext $\sigma$ according to $\Lambda'$, getting $ct$
			It applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
			On input $w$, it applies $\cV_3$ of \cref{proto:BQP} and outputs its result.
	\end{enumerate}
\end{protocol}

@@

	\Ethan{TODO PROOFREAD ME}
	\Ethan{Convention: malicious parties have stars}

	\Ethan{Don't use blackboard bold for provers/verifiers}

	Suppose for the sake of contradiction that some prover $\bbP_{blind}^*$ breaks the soundness of \cref{proto:BlindBQP}.

	Then we use it to construct a prover $\bbP_{MF}^*$ against the soundness guarantees in \cref{proto:BQP}.

	$\bbP_{MF}^*$ simulates \cref{proto:BlindBQP} as $(V_{blind}(x), P_{blind}^*)()$

	\Ethan{Fix interface; $P_{blind}^*$ expects some message from $V$}

	When $\bbP_{blind}^*$ sends $\sigma$, $\bbP_{MF}^*$ computes and sends $\rho=\mathsf{QHE.Dec}_{sk}(\sigma)$ to the verifier. \Ethan{Make observation that $P_{blind}^*$ has $sk$

	By assumption, $\bbV_{Blind}$ has a non-negligible chance to accept after receiving $\sigma$.
	When that happens, $\cV(w)=\cV(\Lambda(\rho))=Acc$.
	So $\bbV_{MF}$ has the same probability to accept after receiving $\rho$.
\end{prf}
